---
title: "Showcase"
subtitle: "Focus on 4CAT"
format: 
  html:
    toc: true
    toc-depth: 4
callout-appearance: simple
execute: 
  cache: true
  eval: true
  echo: true
  message: false
  warning: false
highlight-style: atom-one
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
install.packages("RedditExtractoR")

library(here)
library(tidyverse)
library(RedditExtractoR)
library(easystats)
library(sjmisc)
```

## Background

Practical application of the 4CAT

```{r}
news <- find_subreddits("news")

news %>% glimpse()

news %>% 
  arrange(-subscribers) %>% 
  tibble() %>% head()
```

```{r}
crypto_top_urls <- find_thread_urls(
  subreddit="CryptoCurrency",
  sort_by="top")

crypto_top_urls %>% glimpse()
crypto_top_urls %>% tibble()
```

## 

YouTube Data Tool (YTDT) using the example of Mai Thi Nguyen-Kim ( [{{< fa brands twitter >}}](https://twitter.com/maithi_nk) \| [{{< fa brands instagram >}}](https://www.instagram.com/maithink/) ) and her [{{< fa brands youtube >}}](https://www.youtube.com/c/maiLab)-Channel [maiLab](https://www.youtube.com/c/maiLab).

You can also open this showcase in other interactive and executable environments: [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/chrdrn/dbd_binder/HEAD) [![Google Colab](https://colab.research.google.com/assets/colab-badge.svg)](https://colab.research.google.com/github/chrdrn/dbd_binder/blob/main/session_05-showcase_youtube.ipynb)

## Exercise 1

-   Use the [`Channel Search`](https://tools.digitalmethods.net/netvizz/youtube/mod_channels_search.php) site/function of the `YTDT` to find the (correct) `channel ID` for the <img src="https://raw.githubusercontent.com/FortAwesome/Font-Awesome/6.x/svgs/brands/youtube.svg" width="15" height="15"/> Channel [maiLab](https://www.youtube.com/c/maiLab).
-   Therefore, enter "*maiLab*" in the field `Search query` and download the results as `.csv`.
-   Open the file and search extract the correct channel ID.\
    *Hint:* If in doubt, use [`Channel Info`](https://tools.digitalmethods.net/netvizz/youtube/mod_channel_info.php) function to check if the selected ID matches the channel description.

```{r}
# Load packages
library(readr)
library(tidyverse)

# Import data
channel_list <- read_csv(
  here("content/05-api_access-youtube/data/channelsearch_channels50_2022_11_17-09_54_22.csv"))

# Preview data 
channel_list %>% glimpse()
```

```{r}
# Get channel description with R
channel_list %>%
  filter(title == "maiLab") %>%
  select(id, title, description)
```

## Exercise 2

-   With help of the [`Video List`](https://tools.digitalmethods.net/netvizz/youtube/mod_videos_list.php) site/function of the `YTDT`, get a list of all published videos of the channel `maiLab`.
-   Therefore, use the extracted `channel id` and download the results as `.csv`.
-   Import/preview the data.

```{r}
# Import data: video list
video_list <- read_csv(
  here("content/05-api_access-youtube/data/videolist_channel186_2022_11_17-10_20_11.csv"))

# Preview data 
video_list %>% glimpse()
```

# Exercise 3

-   Perform different explorative data analysis

## Different location parameters

```{r}
# Load additional packages
library(sjmisc) 

# Get distribution parameters for selected variables
video_list %>% 
  select(durationSec, viewCount, likeCount, favoriteCount, commentCount) %>% 
  descr()

```

### More detailed distribution for each variable

```{r}
video_list %>% 
  plot_frq(durationSec, viewCount, likeCount, commentCount, type = "density")
```

## In-depth analysis

Based on the findings of the previous section, let us take a closer look. Interestingly, although most of the varialbes have a left-sloping distribution, there are isolated outliers on the "right" edge.

Therefore, the next goal is to find out which video(s) they are.

### Top 5 videos with the **highest view count**

```{r}
video_list %>% 
  arrange(-viewCount) %>% 
  select(videoTitle, publishedAt, viewCount, likeCount, commentCount) %>% 
  head()
```

### Top 5 videos with the **highest comment count**

```{r}
video_list %>% 
  arrange(-commentCount) %>% 
  select(videoTitle, publishedAt, viewCount, likeCount, commentCount) %>% 
  head()
```
